\documentclass[10pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.55cm,right=1.06cm,bottom=0.9cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\small
\begin{center}
    \huge
    \textbf{Lautaro Lasorsa}\\ 
    \hrulefill
\end{center}

\begin{center}
    lautarolasorsa@gmail.com \textbullet \href{https://www.linkedin.com/in/lautaro-lasorsa/}{LinkedIn: lautaro-lasorsa} \textbullet \href{https://github.com/LautaroLasorsa}{GitHub: LautaroLasorsa}
\end{center}
\begin{center}
    \textbf{Why should you hire me?}
\end{center}

I have a strong foundation in software engineering, data science, and problem solving. I learn new technologies quickly and focus on applying the most appropriate tools and best practices to each project.
\begin{center}
    \textbf{Professional Experience}
\end{center}

\textbf{Autoscheduler.AI} \hfill (Remote)\\
\textbf{Machine Learning Engineer} \hfill July 2025 - Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Designed and implemented agentic AI workflows with LangChain and LangGraph for a warehouse orchestration platform.
    \item Built multi-agent components for conversational data retrieval, analysis, and natural language interaction with business data.
    \item Developed async Python/FastAPI services and integration layers to connect the assistant with SQL Server, Redis, and Cosmos DB.
    \item Implemented data visualization and reporting features using Plotly and matplotlib for automated analytical outputs.
    \item Contributed to production quality practices with Docker, Azure DevOps CI/CD, pytest, Ruff, and type checking.
    \item Developed an agent behavior evaluation suite to assess performance and adaptability in dynamic environments.
    \item Designed and implemented the relational data base schema, following normalization and best pratices.
\end{itemize}

\vspace{0pt}

\textbf{Mutt Data} \hfill (Remote)\\
\textbf{Ssr Data Developer} \hfill February 2025 - June 2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Built ETL pipelines in Google BigQuery to process user engagement data at scale and deliver KPI dashboards for CTR, VTR, completion rate, and time viewed.
    \item Integrated Typesense and TMDB metadata, and used BigQuery table design, CTEs, and window functions to support analytics and search workflows.
    \item Earned the Databricks Certified Data Engineer Associate certification.
\end{itemize}

\vspace{0pt}

\textbf{Composable Finance} \hfill (Remote)\\
\textbf{Cryptography Consultant} \hfill April 2023 - July 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed solutions using Zero Knowledge (ZK) over Gnark.
    \item Implemented the verification of digital signatures over the curve ED-25519 emulating the arithmetic.
    \item Also developed a solution to optimize transactions using graph algorithms and Python.
\end{itemize}

\vspace{0pt}

\textbf{Universidad de Buenos Aires (UBA)}\\
\textbf{Head Class Assistant (JTP)} \hfill March 2025 - Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Led practical sessions on Algorithms and Data Structures and designed midterm exams in a 1 weekly class for 200+ students.
    \item Open to choose morning or afternoon shifts to accomodate with work schedule.
\end{itemize}

\vspace{0pt}

\textbf{Universidad Nacional de La Matanza (UNLaM)}\\
\textbf{Class Assistant} \hfill March 2020 - Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Taught competitive programming to high school (2020-2021) and university students (2022-present) on saturdays using C++, Python, and Kotlin.
    \item Coached 17 teams that competed in the Argentina Programming Tournament (TAP) between 2022 and 2025.
\end{itemize}

\vspace{0pt}
\begin{center}
    \textbf{Competitive Programming and Awards}
\end{center}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item \href{https://icpc.global/ICPCID/DV1XEVUDPG8J}{ICPC World Finalist} (2020: 22nd, 2023: 13th - Bronze Medal, 2024: 17th); Latin America Regional Champion in all three participations.
    \item IOI participant (2017, 2018, 2019), with a Bronze Medal in 2018 (top 50\%).
    \item Speaker at 4 editions of Training Camp Argentina on \textit{Segment Trees}, \textit{SQRT Decomposition}, \textit{Centroid and Heavy-Light Decomposition}, and \textit{Flow Algorithms}.
    \item Built a \href{https://github.com/LautaroLasorsa/competitive-programming-suite}{competitive programming toolkit repository} with reusable commands and setup utilities.
   
\end{itemize}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{Universidad de Buenos Aires (UBA)} 

Data Science Licenciature (Bachelor + Master): 9,09 \hfill March 2019 - December 2024 


\textbf{Universidad Nacional de La Matanza (UNLaM)} 

Computer Engineering (integrated Bachelor + Master): 8.46/10 (in progress, night shift) \hfill March 2019 - December 2027 (expected)


\begin{center}
    \textbf{Technical Skills}
\end{center}

\textbf{Programming:} Python, C++, SQL.

\textbf{Data and AI:} FastAPI, LangChain, LangGraph, BigQuery, Typesense, Plotly, matplotlib.

\textbf{Infrastructure and Quality:} Docker, Azure DevOps CI/CD, Redis, Cosmos DB, pytest, Ruff, static type checking.


\begin{center}
    \textbf{Additional Information}
\end{center}

\textbf{Languages:} English (\href{https://cert.efset.org/Pymcaz}{EF SET 76/100 C2}).

\textbf{Scientific publications:} Since 2021, I have been a member of a research group at UNLaM. We have published 3 papers (
\href{https://github.com/LautaroLasorsa/CONAIISI-2023}{1}, \href{https://github.com/LautaroLasorsa/CONAIISI-2024}{2},
\href{https://github.com/carlucho1/CONAIISI-2024-2}{3}
) about AI applied to IoT. Meetings only on saturdays.
 

% \textbf{Laboratory:} List scientific / research lab techniques or tools [If Applicable]

% \textbf{Interests:} List activities you enjoy that may spark interview conversation




\end{document}
